mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-14 Draft3.Rmd
sum with index
new table

```{r, results='asis'}
term <- quote(hat(y) == hat(b)["0"] + hat(b)["1"]*x["1"])
mathout(term)

# or with greek letters as:
term <- quote(y == beta["0"] + beta["1"]*x["1"] + beta["2"]*x["2"] + ... + beta["i"]*x["i"] + varepsilon["i"])

@@

@@

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Basic elements in mathml", row.names=FALSE, escape=FALSE)
```

```{r arrows, echo=FALSE}
op <- list(twosidearrow=quote(x%<->%b), rightarrow=quote(x%->%y), leftarrow=quote(x%<-%y), uparrow=quote(x%up%y), down=quote(x%down%y), iff=quote(x%<=>%y), rArr=quote(x %=>% y), lArr=quote(x %<=% y), dblup=quote(x %dblup% y), dbldown=quote(x %dbldown% y))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

t <- cbind(Operator=op, Output=m)
knitr::kable(t, caption="Arrows in mathml", row.names=FALSE, escape=FALSE)
```

@@

# fixme: braces not needed when right to *
catmath(a * sum(b))

# Multiplication (capital Pi) is missing
catmath(a * prod(b))

>>>>

```{r, results='asis'}
term <- quote(hat(y) == hat(b)["0"] + hat(b)["1"]*X["1"])
mathout(term)

# or with greek letters as:
term <- quote(y== beta["0"] + beta["1"]*x["1"] + beta["2"]*x["2"] + ... + beta["i"]*x["i"] + varepsilon["i"])

@@

op2 <- list(twosidearrow=quote(x%<->%b), rightarrow=quote(x%->%y), leftarrow=quote(x%<-%y), uparrow=quote(x%up%y), down=quote(x%down%y), iff=quote(x%<=>%y), rArr=quote(x %=>% y), lArr=quote(x %<=% y), dblup=quote(x %dblup% y), dbldown=quote(x %dbldown% y))
m2 <- lapply(op2, FUN=mathjax, flags=list(cat=FALSE))

op2 <- as.character(op2)
if(knitr::is_latex_output())
  op2 <- sapply(op2, FUN=knitr:::escape_latex)
if(knitr::is_html_output())
  op2 <- sapply(op2, FUN=knitr:::escape_html)

@@

t <- cbind(Operator=op, Output=m, Operator=op2, Output=m2)
knitr::kable(t, caption="Basic elements in mathml", row.names=FALSE, escape=FALSE)
```

@@

# fixme: braces not needed when right to *
catmath(a * sum(b[i]))

# Multiplication (capital Pi) is missing
catmath(a * prod(b[i]))
